Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Update todo
Add beginning of scientific study disposition

% Thursday:
% TODO: Fix citings like they appear in the example thesis
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture
% TODO: Introduction references
% TODO: Write introduction

@@

\section{Utility in real world applications}

>>>>

% Thursday:
% TODO: Fix citings like they appear in the example thesis
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: Introduction references
% TODO: Write Collision study implementation section
    % TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

@@

\section{Scientific study: Where does this fit in the general Scietific scope of things}

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy.
When we have the fundamental
we can proceed with building modeling (Parish Müller, procedural building modeling). Other challenges include infering or guessing building height. () have presented a method for inferring building height from the building footprint alone, with surprising accuracy.
